Effects of the body force on the evacuation dynamics

### 2020-02-04 paper.tex
agregue una hipotesis adicional
agregue el abstract y mejore el grafico de los triangulos

@@

>>>>

The Social Force Model (SFM) is a suitable model for describing crowds behaviors.
In this research, we analyze the role of the body force in the original SFM. 
We focus on the parameter associated with the body stiffness ($k_n$) and its impact on the pedestrian dynamics in two different geometries: bottleneck and corridor.
Increasing $k_n$ produces opposite effects depending on the geometry analyzed. Pedestrians move faster in a bottleneck, but they move slower in corridors as $k_n$ increases. The improvement in the bottleneck geometry is because increasing the stiffness reduces the contacts among pedestrians. This effect reduces the number of blocking clusters close to the exit door (which is critical to improving the evacuation). The slow down in the corridor geometry occurs because when $k_n$ increases, the crowd behaves like a solid-granular-system in which the friction interaction with the wall determines the velocity of the whole crowd. We have also explored the dimensionless parameters that arise from the reduced-in-units equation of motion and tune them to reproduce the qualitative behavior of the empirical fundamental diagram.

@@

\item 5) No contemplamos los efectos de la turbulencia. Solo nos interesan los comportamientos macroscopicos. Por eso buscamos reproducir comportamientos macroscopicos con el modelo mas simple posible.
